\mytitle

### 2021-12-07 paper.tex
extend text

\newcommand{\mytitle}{The performance gain of instruction-level parallelism on the evaluation of special functions}
\newcommand{\myauthor}{Alexander Voigt}

@@

>>>>

\newcommand{\mytitle}{The performance gain of instruction-level parallelism on the evaluation of special functions}
\newcommand{\myauthor}{Alexander Voigt}
\newcommand{\Li}{\operatorname{Li}_2}

@@

As an application we consider the implementation of the real
dilogarithm, which appears in many physics applications, for example
in the calculation of quantum corrections in quantum electrodynamics.
The real dilogarithm is defined as
%
\begin{align}
  \Li(x) &= -\int_0^x \frac{\log(1-t)}{t}dt, &
  &(x<1).
\end{align}
%
For $|x|<1$ the real dilogarithm has the series representation
%
\begin{align}
  \Li(x) = \sum_{k=1}^\infty \frac{x^k}{k^2}.
\end{align}
%
Further series representations exists, for example
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty \frac{B_k}{(k+1)!} [-\log(1-x)]^{k+1},
\end{align}
%
where $B_k$ are the Bernoulli numbers.  A representation in terms
of Chebyshev polynomials also exists \cite{luke},
%
\begin{align}
  \Li(x) = \sum_{k=0}^\infty a_n T_n^*(x),
\end{align}
%
which is used for example in the ROOT program library \cite{root}.
